---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
````{r}
library(dplyr)
options(digits = 3)
activity = read.csv("./activity.csv")
head(activity)
str(activity)
```
## What is mean total number of steps taken per day?

The total number of steps taken per day and its histogram is shown as follows.

```{r}
steps_daily = summarize(group_by(activity, date), sum=sum(steps, na.rm = TRUE))
steps_daily_mean = mean(steps_daily$sum, na.rm = TRUE)
steps_daily_median = median(steps_daily$sum, na.rm = TRUE)
hist(steps_daily$sum, 
     xlab="the total number of steps taken per day", 
     ylab="days",
     main="Histogram of the total number of steps taken per day")
```

The mean of the total number of steps taken per day is `r steps_daily_mean` and 
the median of the total number of steps taken per day is `r steps_daily_median`

## What is the average daily activity pattern?

The time series plot of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis) is as follows.

```{r}
steps_interval = summarize(group_by(activity, interval), mean=mean(steps, na.rm = TRUE))
plot(mean ~ interval, steps_interval, type='l', ylab="average steps taken")
```

and interal `r steps_interval[which.max(steps_interval$mean),]$interval` contains the maximum number of steps.

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
